Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-23 manuscript_results.Rmd
update

# Prepare a list to hold your plots
bric_plots <- list()

for (i in 1:4) {
  # 1) Join the WIS and BRIC data
  WIS_bric <- inner_join(
    WIS_dataframes[[i]],
    bric_by_state,
    by = "STATE"
  )

  # 2) Fit the linear model
  model <- lm(
    percentage_improvement ~ weighted_mean_z_bric.infrastructure,
    data = WIS_bric
  )
  ms <- summary(model)

  # 3) Extract R² and p‐value
  r2 <- round(ms$r.squared, 3)
  p  <- signif(ms$coefficients[2, 4], 3)

  # 4) Build the ggplot
  p <- ggplot(WIS_bric,
              aes(x = weighted_mean_z_bric.infrastructure,
                  y = percentage_improvement)) +
    geom_point(color = "steelblue", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color = "darkred") +
    labs(
      title    = paste("Regression","Target Week", i),
      subtitle = paste0("R² = ", r2, "   p = ", p),
      x        = "BRIC infrastructure (2015)",
      y        = "Difference"
    ) +
    theme_minimal()

  # 5) Store it
  bric_plots[[i]] <- p
}

>>>>

# Prepare a list of plots
bric_plots <- list()

for (i in 1:4) {
  # Join the WIS and BRIC data
  WIS_bric <- inner_join(
    WIS_dataframes[[i]],
    bric_by_state,
    by = "STATE"
  )

  # Fit the linear model
  model <- lm(
    percentage_improvement ~ weighted_mean_z_bric.infrastructure,
    data = WIS_bric
  )
  ms <- summary(model)

  # Extract R-squared and p-value
  r2 <- round(ms$r.squared, 3)
  p  <- signif(ms$coefficients[2, 4], 3)

  # Build the ggplot
  p <- ggplot(WIS_bric,
              aes(x = weighted_mean_z_bric.infrastructure,
                  y = percentage_improvement)) +
    geom_point(color = "steelblue", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color = "darkred") +
    labs(
      title    = paste("Regression","Target Week", i),
      subtitle = paste0("R² = ", r2, "   p = ", p),
      x        = "BRIC infrastructure (2015)",
      y        = "Difference"
    ) +
    theme_minimal()

  # Store it
  bric_plots[[i]] <- p
}
